---
title: "IIT Delhi-Leiden Pilot"
output:
  html_document:
    df_print: paged
  html_notebook: default
  pdf_document:
    latex_engine: xelatex
---

Preliminary analyses over pilot data to see if it makes sense.

```{r preparation, include=FALSE}
library(dplyr)
library(tidyr)
library(stringr)
library(ggplot2)
library(reshape2)
library(ggstatsplot)
library(afex)
library(GGally)
library(lme4)


# Import data
full_df <- read.csv('../data/20210930.tsv', sep='\t', header=TRUE, skipNul=TRUE, stringsAsFactors=FALSE, fileEncoding = 'UTF-16LE')
full_df <- full_df[3:nrow(full_df),]

# Prepare dataset
cols_to_covert_num <- c(colnames(full_df)[19:486], "Duration..in.seconds.")
full_df[cols_to_covert_num] <- sapply(full_df[cols_to_covert_num],as.numeric)

# Remove unsuitable data
full_df <- subset(full_df, Duration..in.seconds. > 600)
full_df <- subset(full_df, Progress == 100)

```

```{r conversion, include=FALSE, cache=FALSE}

for (subj in 1:nrow(full_df)) {
  for (robot in 1:18){
    robot_name <- paste("X", robot, sep="")

    sumlike <- sum(get(paste("X", robot, "_Q1_1", sep=""), full_df[subj,]), get(paste("X", robot, "_Q1_1.1", sep=""), full_df[subj,]), na.rm=TRUE)
    full_df[[paste0(robot_name, "_like")]][subj] <- sumlike

    phys_sim <- sum(get(paste("X", robot, "_Q2_1", sep=""), full_df[subj,]), get(paste("X", robot, "_Q2_1.1", sep=""), full_df[subj,]), na.rm=TRUE)
    full_df[[paste0(robot_name, "_phys_sim")]][subj] <- phys_sim
    
    think_hum <- sum(get(paste("X", robot, "_Q3_1", sep=""), full_df[subj,]), get(paste("X", robot, "_Q3_1.1", sep=""), full_df[subj,]), na.rm=TRUE)
    full_df[[paste0(robot_name, "_think_hum")]][subj] <- think_hum
    
    friendly <- sum(get(paste("X", robot, "_Q4_1", sep=""), full_df[subj,]), get(paste("X", robot, "_Q4_1.1", sep=""), full_df[subj,]), na.rm=TRUE)
    full_df[[paste0(robot_name, "_friendly")]][subj] <- friendly
    
    creepy <- sum(get(paste("X", robot, "_Q5_1", sep=""), full_df[subj,]), get(paste("X", robot, "_Q5_1.1", sep=""), full_df[subj,]), na.rm=TRUE)
    full_df[[paste0(robot_name, "_creepy")]][subj] <- creepy
    
    plan_indep <- sum(get(paste("X", robot, "_Q6_1", sep=""), full_df[subj,]), get(paste("X", robot, "_Q6_1.1", sep=""), full_df[subj,]), na.rm=TRUE)
    full_df[[paste0(robot_name, "_plan_indep")]][subj] <- plan_indep
    
    feel_emo <- sum(get(paste("X", robot, "_Q7_1", sep=""), full_df[subj,]), get(paste("X", robot, "_Q7_1.1", sep=""), full_df[subj,]), na.rm=TRUE)
    full_df[[paste0(robot_name, "_feel_emo")]][subj] <- feel_emo
    
    vacuum <- sum(get(paste("X", robot, "_Q8_1", sep=""), full_df[subj,]), get(paste("X", robot, "_Q8_1.1", sep=""), full_df[subj,]), na.rm=TRUE)
    full_df[[paste0(robot_name, "_vacuum")]][subj] <- vacuum
    
    cook <- sum(get(paste("X", robot, "_Q9_1", sep=""), full_df[subj,]), get(paste("X", robot, "_Q9_1.1", sep=""), full_df[subj,]), na.rm=TRUE)
    full_df[[paste0(robot_name, "_cook")]][subj] <- cook
    
    care_family <- sum(get(paste("X", robot, "_Q10_1", sep=""), full_df[subj,]), get(paste("X", robot, "_Q10_1.1", sep=""), full_df[subj,]), na.rm=TRUE)
    full_df[[paste0(robot_name, "_care_family")]][subj] <- care_family

    touch <- sum(get(paste("X", robot, "_Q11_1", sep=""), full_df[subj,]), get(paste("X", robot, "_Q11_1.1", sep=""), full_df[subj,]), na.rm=TRUE)
    full_df[[paste0(robot_name, "_touch")]][subj] <- touch
    
    want_to_have <- sum(get(paste("X", robot, "_Q12_1", sep=""), full_df[subj,]), get(paste("X", robot, "_Q12_1.1", sep=""), full_df[subj,]), na.rm=TRUE)
    full_df[[paste0(robot_name, "_want_to_have")]][subj] <- want_to_have
    
    dictator_offer <- sum(get(paste("X", robot, "_Q13", sep=""), full_df[subj,]), get(paste("X", robot, "_Q13.1", sep=""), full_df[subj,]), na.rm=TRUE)
    if (full_df[subj,"Country"] == "India") {
      dictator_offer <- dictator_offer / 250
    } else {
      dictator_offer <- dictator_offer / 10
    }
    full_df[[paste0(robot_name, "_dictator_offer")]][subj] <- dictator_offer
    
    
  }
}


data_long <- gather(full_df, QuestionType, value, X1_like:X18_dictator_offer, factor_key=TRUE)
data_long$RobotType <- gsub(".*[X]([^_]+)[_].*", "\\1", data_long$QuestionType)
data_long$Question <- sub("^[^_]*_", "", data_long$QuestionType)
data_long$RobotType <- as.factor(data_long$RobotType)
data_long$Question <- as.factor(data_long$Question)
data_long$RobotType <- factor(data_long$RobotType, levels = as.character(1:18))

data_wide <- dcast(data_long, ResponseId + Country + RobotType ~ Question, value.var="value")

```

# General sample characteristics

The pilot data contains `r length(unique(data_long$ResponseId))` subjects.

```{r echo=FALSE, fig.height=7, fig.width=11, message=FALSE, warning=FALSE, cache=TRUE}
ggwithinstats(
  data = data_wide,
  x = RobotType,
  y = like,
  type = "parametric",
  xlab = "Robot number",
  ylab = "I like this robot",
  title = "Likeability of the robots",
  package = "beyonce",
  palette = "X95",
  bf.message = TRUE,
  centrality.plotting = TRUE,
  subject.id = "ResponseId"
)


ggwithinstats(
  data = data_wide,
  x = RobotType,
  y = want_to_have,
  type = "parametric",
  xlab = "Robot number",
  ylab = "I would like to have this robot",
  title = "Do you want to have this robot?",
  package = "beyonce",
  palette = "X95",
  bf.message = TRUE,
  centrality.plotting = TRUE,
  subject.id = "ResponseId"
)


ggwithinstats(
  data = data_wide,
  x = RobotType,
  y = touch,
  type = "parametric",
  xlab = "Robot number",
  ylab = "I would like to be touched by this robot",
  title = "Willingness to be touched by robots",
  package = "beyonce",
  palette = "X95",
  bf.message = TRUE,
  centrality.plotting = TRUE,
  subject.id = "ResponseId"
)

```


# Some preliminary correlations


```{r corrs, echo=FALSE, fig.height=9, fig.width=9}
ggcorrmat(
  data = data_wide[,3:15],
  colors = c("#B2182B", "white", "#4D4D4D"),
  title = "Correlogram over all variables"
)

```

```{r corrs1, echo=FALSE, fig.height=6, fig.width=7}

ggscatterstats(
  data = data_wide,
  x = friendly,
  y = creepy,
  xlab = "Rated friendliness",
  ylab = "Rated creepiness",
  title = "Friendliness and creepiness"
)
```

```{r corrs2, echo=FALSE, fig.height=6, fig.width=7}

ggscatterstats(
  data = data_wide,
  x = like,
  y = dictator_offer,
  xlab = "Rated likeability",
  ylab = "Proportion offered in dictator game",
  title = "Likeability and dictator game behavior"
)

```


```{r corrs4, echo=FALSE, fig.height=6, fig.width=7}

ggscatterstats(
  data = data_wide,
  x = care_family,
  y = dictator_offer,
  xlab = "I would allow this robot to take care of my family",
  ylab = "Proportion offered in dictator game",
  title = "Allowing a robot to care for family and dictator game behavior"
)

```

## Dictator game behavior

```{r country, echo=FALSE, fig.height=6, fig.width=7}

# plot
ggbetweenstats(
  data = data_wide,
  x = Country,
  y = dictator_offer,
  title = "Proportion offered by country"
)

```

```{r corrs3, echo=FALSE, fig.height=6, fig.width=7}

ggscatterstats(
  data = data_wide,
  x = feel_emo,
  y = dictator_offer,
  xlab = "Rated ability to feel emotions",
  ylab = "Proportion offered in dictator game",
  title = "Ability to feel emotions and dictator game behavior"
)


ggscatterstats(
  data = subset(data_wide, feel_emo>5 & feel_emo<95 & dictator_offer >.05 & dictator_offer <.95),
  x = feel_emo,
  y = dictator_offer,
  xlab = "Rated ability to feel emotions",
  ylab = "Proportion offered in dictator game",
  title = "Ability to feel emotions and dictator game behavior"
)


```

There is a significant positive relationship between the perceived ability to feel pain and the proportion of the stake awarded in a dictator game. But for a thorough analysis we will need a linear model accounting for subject.

### Hierarchical linear model

```{r lin_model_dictator_emo, echo=FALSE}
mixed.lmer <- lmer(dictator_offer ~ feel_emo + (1|ResponseId), data = data_wide)
summary(mixed.lmer)

```




